Honors Draft

### 2020-02-10 chapters/article-draft.Rmd
fix table

<!-- \begin{table}[h] -->
<!-- \centering -->
<!-- \begin{tabular}{lr} -->
<!--   \toprule -->
<!-- Parameter & meaning \\ -->
<!--   \midrule -->
<!-- beta[1] &  median household income \\ -->
<!--   beta[2] &  percent residents identified as white alone \\ -->
<!--   beta[3] &  area of 10 minute walk isochrone from population-weighted block group centroid \\ -->
<!--   beta[4] &  percent residents with a high school diploma \\ -->
<!--   beta[5] &  percent residents with a bachelor's degree \\ -->
<!--   beta[6] &  percent of residents who rent their residence \\ -->
<!--   beta[7] &  percent of residents without a vehicle \\ -->
<!--   beta[8] &  percent of residents who speak only English \\ -->
<!--   beta[9] &  percent of residents identified as foreign \\ -->
<!--   beta[10] & employment density \\ -->
<!--   beta[11] & percent of jobs in block group for white employees \\ -->
<!--   beta[12] & percent of jobs in block group for male employees \\ -->
<!--   beta[13] & percent of jobs in block group for employees with no college degree \\ -->
<!--   beta[14] &  percent of jobs in block group for employees who make less than $40,000 \\ -->
<!--   beta[15] &  percent of jobs in block group for employees under age 30 \\ -->
<!--   beta[16] &  median age \\ -->
<!--   beta[17] &  percent residents who use transit to commute to work \\ -->
<!--   beta[18] &  population density \\ -->
<!--    \bottomrule -->
<!-- \end{tabular} -->
<!-- \caption{List of covariates} -->
<!-- \end{table} -->

>>>>

\begin{table}[H]
\centering
\begin{tabular}{ll} \toprule
    Parameter & Meaning \\ \midrule
    beta[1] & median household income \\ 
    beta[2] & percent residents identified as white alone \\ 
    beta[3] &  area of 10 minute walk isochrone from population-weighted block group centroid \\
    beta[4] &  percent residents with a high school diploma \\
    beta[5] &  percent residents with a bachelor's degree \\
    beta[6] &  percent of residents who rent their residence \\
    beta[7] &  percent of residents without a vehicle \\
    beta[8] &  percent of residents who speak only English \\
    beta[9] &  percent of residents identified as foreign \\
    beta[10] & employment density \\
    beta[11] & percent of jobs in block group for white employees \\
    beta[12] & percent of jobs in block group for male employees \\
    beta[13] & percent of jobs in block group for employees with no college degree \\
    beta[14] & percent of jobs in block group for employees who make less than \$40,000 \\
    beta[15] & percent of jobs in block group for employees under age 30 \\
    beta[16] & median age \\
    beta[17] & percent residents who use transit to commute to work \\
    beta[18] & population density \\
    \bottomrule
 \hline
\end{tabular}
\caption{List of covariates}
\end{table}
